---
title: "CaitlinRowley - Blog Post 4"
author: "Caitlin Rowley"
date: 10/30/2022
editor: visual
---

I have switched data sets for future blog posts. I will be using open-ended survey responses from a 1996 study titled *Survey of Gun Owners in the United States*.

For the study, respondents were asked six qualifying questions related to: (1) gun ownership, (2) gun-carrying practices, (3) gun display against the respondent, (4) gun use in self-defense against animals, (5) gun use in self-defense against people, and (6) other weapons used in self-defense. A "yes" response to a qualifying question led to a series of additional questions on the same topic as the qualifying question.

The open-ended responses include descriptions specifically related to the following questions: (1) where the respondent was when he or she displayed a gun (in self-defense or otherwise), (2) specific reasons why the respondent displayed a gun, (3) how the other individual reacted when the respondent displayed the gun, (4) how the individual knew the respondent had a gun, (5) whether the police were contacted for specific self-defense events, and (6) if not, why not.

I will focus on the following research question: Can we identify the most common circumstance in which respondents displayed a gun? I am hoping that "circumstance" can include references to both the catalyst in the situation and the environment.

```{r}
# install packages:

install.packages("RColorBrewer")
install.packages("stopwords")

# load libraries: 

library(tidyverse)
library(dplyr)
library(quanteda)
library(magrittr)
library(RColorBrewer)
library(wordcloud)
library(tidytext)
library(stopwords)
library(tm)
library(quanteda.textplots)
library(tokenizers)

# read in data:

Survey <- read_csv("C:\\Users\\caitr\\OneDrive\\Documents\\DACSS\\DACSS 679\\DACSS 697\\DACSS 697 - Survey.csv", col_names = TRUE)

#rename columns:

names(Survey) <- c('Respondent_ID','Survey_Question', 'Code', 'Open_Ended_Response')
print(Survey)

# remove duplicate observations: 

Survey_unique <- distinct(Survey)

Survey_unique %>% 
    separate_rows(Open_Ended_Response) %>% 
    distinct() %>%
    nrow

```

There are 812 rows in this data frame and 4 columns. The four columns represent the following variables: survey respondent ID ('Respondent_ID), survey question ('Survey_Question'), response code ('Code'), and verbatim open-ended responses ('Open_Ended_Responses'). Each of the 812 rows now represents a unique observation. Additionally, there are 8134 unique words across all open-ended responses.

I will next create a corpus and remove both capitalization and punctuation from all open-ended responses.

```{r}
# create a corpus:

Survey_corpus <- corpus(Survey_unique$Open_Ended_Response)
head(Survey_corpus)

# tokenize, remove capitalization and punctuation:

Survey_tokens <- tokens(Survey_corpus, 
    remove_punct = T)
Survey_tokens <- tokens_tolower(Survey_tokens)
head(Survey_tokens)

# remove stopwords separately: 

Survey_tokens_stopwords <- tokens_select(Survey_tokens,
                                       pattern = stopwords("en"),
                                       selection = "remove")

```

I will next extract features from my corpus by creating a document feature matrix. From there, I will be able to generate data visualizations.

```{r}
# create document feature matrix:

Survey_dfm <- dfm(Survey_tokens_stopwords)

# identify 10 most common words:

topfeatures(Survey_dfm, 10)

# create a wordcloud:

textplot_wordcloud(Survey_dfm, min_count = 5, max_words = 50, random_order = FALSE)
```

Next, I will generate a feature co-occurrence matrix:

```{r}
# create a dfm that is limited to words that appear frequently (more than 30% of responses).

Survey_dfm_freq <- dfm_trim(Survey_dfm, min_termfreq = 30)
Survey_dfm_freq <- dfm_trim(Survey_dfm_freq, min_docfreq = .3, docfreq_type = "prop")

# use dfm to create a feature co-occurring matrix:

Survey_fcm <- fcm(Survey_dfm_freq)

# check dimensions:

dim(Survey_fcm)

```

The first time I ran this chunk of code, the dimensions of the feature co-occurring matrix were shown to be 395 rows by 395 columns. After re-running the codes after reopening R, the dimensions are now showing as 0 rows by 0 columns.

```{r}
# identify the top 30 features from my feature co-occurrence matrix:

myFeatures <- names(topfeatures(smaller_fcm, 30))

# retain only the top 30 features as part of a new matrix:

even_smaller_fcm <- fcm_select(smaller_fcm, pattern = myFeatures, selection = "keep")

# check dimensions:

dim(even_smaller_fcm)

# compute size weight for vertices in network
size <- log(colSums(even_smaller_fcm))

# create plot
textplot_network(even_smaller_fcm, vertex_size = size / max(size) * 3)

```

Next, I will apply dictionary approaches (most likely sentiment analysis) to my data.
